On the presentation of orthogonal groups over polynomial rings

### 2019-05-27 dl-paper.tex
Proved 4.3

\begin{lemma} \label{lem:SRsharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P_\beta\left(\tfrac{m'}{1 + am}\right). \] \end{lemma}
\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
  S_\alpha(a, g_0) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
The assertion now follows from the preceding corollary.
\end{proof}

@@

\begin{lemma} \label{lem:SRobtuse} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a, b\in A$ the element \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
 belongs to $P_\alpha\left(\tfrac{m - \epsilon bm'}{1+am}\right)$, where $\epsilon = N_{\alpha, -\beta}$.
\end{lemma}
\begin{proof} Set $c = 1 + \epsilon a b m'$, $s_0 = \langle a, m \rangle$, $s_1 = \langle \epsilon am', -bc^{-1} \rangle$.
From the definition of $S_\alpha(a, -)$ we obtain that
 \begin{multline} \label{eq:SRobtuse-computation}
 S_\alpha(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
 = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) = \\
 = x_{-\beta}(m'X) \cdot x_{\alpha - \beta}(\epsilon am') \cdot x_{\beta - \alpha}(-bc^{-1}) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 = x_{-\beta}(m'X) \cdot x_{\beta - \alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}\left(\epsilon acm'\right) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 =  x_{\beta - \alpha}(-b) \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(-\epsilon bm'X) \cdot s_1 \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot x_{-\alpha}\left(\tfrac{cmX}{1+am}\right) \cdot s_0 = \\
 = x_{\beta-\alpha}(-b) \cdot x_{-\beta}\left(m'X(1 - \epsilon abm'c^{-1})\right) \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot s_1 \cdot s_0 \cdot x_{-\alpha}\left(-\epsilon bm' X + \tfrac{cmX}{1+am}\right).
\end{multline}
Denote by $h_0$ the product of all terms except the first and the last one in the above formula. It is clear that $h_0$ lies in $P_\alpha(0)$. Using~\cref{K-a-b} we can decompose $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$. The required assertion now follows from \eqref{eq:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:
\begin{multline} \nonumber
 x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\
  = x_{\beta - \alpha}(b) \cdot S_\alpha(a, g_0) \cdot x_{\beta-\alpha}(-b) \cdot h_0 \cdot x_{-\alpha}\left(\tfrac{m -\epsilon bm'}{1+am}\right) \in P_\alpha(\tfrac{m -\epsilon bm'}{1+am}). \qedhere
\end{multline}
\end{proof}

\subsection{The proof of the injectivity theorem}
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
For shortness we also write $G_M^0$ instead of $\overline{\St}(\Phi, A, M)$.
\[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]) &  } \] 
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
$p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$.
It is clear that this action is well defined.
Denote by $\overline{V}$ the set of orbits of the action of $G_M^0$ on $V$.
Whenever $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$.

@@

\begin{lemma}\label{lem:orbit-action} Let $\Phi$ be a simply-laced root system of rank $\geq 3$ and $(A, M)$ be a local pair. 
Then for any $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined total orbit function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is also a representative of the same orbit as $(g, h, u)$.

 Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on the choice of a representative.
 Let $(g, h_1, u) \sim (g, h_2, u)$ be elements of the same orbit for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ belong to $P_\alpha(*)$.
 By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in G^0_M$, moreover, 
  $p(g, h_1, u)^{-1} \cdot p(g, h_2, u) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
 By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
 From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, A[X, X^{-1}])$ we obtain that
 the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
 By~\cref{thmStein} the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and therefore is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS}. Thus, we have obtained that $h_0 \in Z_\alpha(A, M)$ and hence that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
 \begin{multline} \nonumber
  t_\alpha(aX^{-1})(g, h_1, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
  \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(g, h_2, u). \qedhere
 \end{multline} \end{proof}

\begin{prop}
 The operators $T_\alpha(aX^{-1})$ satisfy relations $\text{R1}_1, $ $\text{R2}_1$.
\end{prop}
\begin{proof}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
Invoking~\cref{SR:additivity} once again we obtain that
\begin{multline} \nonumber t_\alpha(bX^{-1}) t_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
t_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim t_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline} 
which implies the assertion for $\text{R1}_1$.

Now let us verify $\text{R2}_1$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$. 
Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$ (cf. the first part of the proof of~\cref{lem:orbit-action}). Now for $a, b \in A$ set $\epsilon = N_{?, ?}$ and $c = 1 + \epsilon abm'$.
It is clear that $\alpha$ and $\alpha+\beta$ form a sharp angle.
\begin{multline} \nonumber
[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
 T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\tfrac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
 \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
 = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
 \begin{multline} \nonumber
 h' = h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\tfrac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\ \sim  h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\tfrac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
 = h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\tfrac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\tfrac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
 h\cdot x_{\alpha + \beta}\left(\tfrac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
\end{multline}
\end{proof}

>>>>

\begin{lemma} \label{SR:sharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right). \] \end{lemma}
\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbayev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am). \end{multline}
The assertion now follows from the preceding corollary.
\end{proof}

@@

\begin{lemma} \label{SR:obtuse} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a, b\in A$ the element \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
 belongs to $P_\alpha\left(\tfrac{m - \epsilon bm'}{1+am}\right)$, where $\epsilon = N_{\alpha, -\beta}$.
\end{lemma}
\begin{proof} Set $c = 1 + \epsilon a b m'$, $s_0 = \langle a, m \rangle$, $s_1 = \langle \epsilon am', -bc^{-1} \rangle$.
From the definition of $S_\alpha(a, -)$ we obtain that
 \begin{multline} \label{eq:SRobtuse-computation}
 S_\alpha(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
 = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) = \\
 = x_{-\beta}(m'X) \cdot x_{\alpha - \beta}(\epsilon am') \cdot x_{\beta - \alpha}(-bc^{-1}) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 = x_{-\beta}(m'X) \cdot x_{\beta - \alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}\left(\epsilon acm'\right) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 =  x_{\beta - \alpha}(-b) \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(-\epsilon bm'X) \cdot s_1 \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot x_{-\alpha}\left(\tfrac{cmX}{1+am}\right) \cdot s_0 = \\
 = x_{\beta-\alpha}(-b) \cdot x_{-\beta}\left(m'X(1 - \epsilon abm'c^{-1})\right) \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot s_1 \cdot s_0 \cdot x_{-\alpha}\left(-\epsilon bm' X + \tfrac{cmX}{1+am}\right).
\end{multline}
Denote by $h_0$ the product of all terms except the first and the last one in the above formula. It is clear that $h_0$ lies in $P_\alpha(0)$. Using~\cref{K-a-b} we can decompose $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$. The required assertion now follows from \eqref{eq:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:
\begin{multline} \nonumber
 x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\
  = x_{\beta - \alpha}(b) \cdot S_\alpha(a, g_0) \cdot x_{\beta-\alpha}(-b) \cdot h_0 \cdot x_{-\alpha}\left(\tfrac{m -\epsilon bm'}{1+am}\right) \in P_\alpha(\tfrac{m -\epsilon bm'}{1+am}). \qedhere
\end{multline}
\end{proof}

\subsection{The proof of the injectivity theorem}
Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
For shortness we also write $G_M^0$ instead of $\overline{\St}(\Phi, A, M)$.
\[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]) &  } \] 
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times \St(\Phi, A[X\inv]) \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
$p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}$ belongs to $\overline{G}_M^{\geq 0}$.
We let $h_0 \in G_M^0$ act on $V$ on the right by $(g, h, u) \cdot h_0 = (g, h \cdot i_-(h_0), u)$.
It is clear that this action is well defined.
Denote by $\overline{V}$ the set of orbits of the action of $G_M^0$ on $V$.
Whenever $(g, h_1, u)$ and $(g, h_2, u)$ lie in the same orbit we use the notation $(g, h_1, u) \sim (g, h_2, u)$.

@@

\begin{lemma}\label{lem:orbit-action} Let $(A, M)$ be a local pair. 
Then for any $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined total orbit function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is also a representative of the same orbit as $(g, h, u)$.

 Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on a choice of representative.
 Let $(g, h_1, u) \sim (g, h_2, u)$ be elements of the same orbit for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ belong to $P_\alpha(*)$.
 By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in G^0_M$, moreover, 
  $p(g, h_1, u)^{-1} \cdot p(g, h_2, u) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
 By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
 From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, A[X, X^{-1}])$ we obtain that
 the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
 By~\cref{thmStein} the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and therefore is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS}. Thus, we have obtained that $h_0 \in Z_\alpha(A, M)$ and hence that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
 \begin{multline} \nonumber
  t_\alpha(aX^{-1})(g, h_1, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
  \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(g, h_2, u). \qedhere
 \end{multline} \end{proof}

The following proposition is directly inspired by~\cite[Proposition~4.3]{Tu83}.
\begin{prop} The operators $T_\alpha(aX^{-1})$ satisfy all relations $\text{R1}_1, $ $\text{R2}_1$ and relations $\text{R3}_{1,1}$ in the special case when $\alpha, \beta$ form a sharp angle.
\end{prop}
\begin{proof}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline}

Let us verify $\text{R2}_1$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$. Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$ (cf. the first part of the proof of~\cref{lem:orbit-action}). Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta}$ and $c = 1 - \epsilon abm'$.
Applying~\cref{SR:obtuse} to a pair of roots $\alpha, \alpha+\beta$ we obtain that 
\begin{multline} \nonumber
[T_\beta(b), T_\alpha(aX^{-1})] \left(g, h, u \right) = \\
 = T_\beta(b) T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right) , u (1 - am) \right) \sim \\ \sim T_\beta(b) \cdot T_\alpha(aX^{-1}) \left( x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g, h \cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc), u (1 - am) \right) = \\ = \left([x_\beta(b), x_\alpha(aX^{-1})] g, h', u c\right) \sim T_{\alpha+\beta}(-\epsilon abX^{-1})(g, h, u),\end{multline} 
 where the last equivalence is obtained as follows:
 \begin{multline} \nonumber
 h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\beta}(bc)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\ = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim \\ \sim h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right).
\end{multline}

Let us prove $\text{R3}_{1,1}$ in the special case when $\alpha$ and $\beta$ form a sharp angle. As before, we can assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\beta}(m'))$ for some $m, m' \in M$. Set $\epsilon = N_{\alpha,-\beta}$.
Applying~\cref{SR:sharp} we obtain that
\begin{multline} \label{eq:sharp-formula1}
 T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
 T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
 \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am'),\ u(1 + am)\right) = \\
 = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline} 
 \begin{multline} \label{eq:sharp-formula2}
 h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-\epsilon am') \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
 = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
 \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
\end{multline}
The expressions in the right-hand sides of~\eqref{eq:sharp-formula1}--\eqref{eq:sharp-formula2} are clearly symmetric under transposition $(a, \alpha) \leftrightarrow (b, \beta)$, which implies $\text{R3}_{1,1}$.
\end{proof}
